Analysis plan

### 2023-05-24 02. Design/MSG-P2312-Analysis Plan-1-clusters.rmd
Update MSG-P2312-Analysis Plan-1-clusters.rmd
Updated formatting
Update MSG-P2312-Analysis Plan-1-clusters.rmd
Updated to only be an indicator if all offsite or onsite flexible team members meet the two days per pay period requirement

1.  **All remote** - All team members are100% remote
2.  **Routine teleworker** - All team members have
    `position_category_description`'s *Onsite Flexible* or *Offsite* and
    work at least two two days per pay period onsite.
3.  **Onsite Flexible** - All team members are *Onsite Flexible* as
    defined by `position_category_description` in the roster data
4.  **Offsite** - All team members are *Offsite* as defined byteam
    members `position_category_description` in the roster data
5.  **Onsite Required** - All team members are *Onsite Required* as
    defined by `position_category_description` in the roster data
6.  Mixed position categories - Team members are different position
    categories as as defined by `position_category_description` in the
    roster data
7.  **Primarily remote** - Teams that work remotely above the 95th
    percentile <!-- could be 75th -->
8.  **Mostly remote** - Teams that work remotely between the median and
    the 95th percentile <!-- could be 75th -->
9.  **Mostly onsite** - Teams that work remotely between 5th percentile
    and the median <!-- could be 25th -->
10. **Primarily onsite** - Teams that work remotely below the 5th
    percentile <!-- could be 75th -->

>>>>

1.  **All remote** - All team members are100% remote
2.  **Routine teleworker** - All team members who have
    `position_category_description`'s *Onsite Flexible* or *Offsite* and
    work at least two two days per pay period onsite.
3.  **Onsite Flexible** - All team members are *Onsite Flexible* as
    defined by `position_category_description` in the roster data
4.  **Offsite** - All team members are *Offsite* as defined byteam
    members `position_category_description` in the roster data
5.  **Onsite Required** - All team members are *Onsite Required* as
    defined by `position_category_description` in the roster data
6.  **Mixed position categories** - Team members are different position
    categories as as defined by `position_category_description` in the
    roster data
7.  **Primarily remote** - Teams that work remotely above the 95th
    percentile <!-- could be 75th -->
8.  **Mostly remote** - Teams that work remotely between the median and
    the 95th percentile <!-- could be 75th -->
9.  **Mostly onsite** - Teams that work remotely between 5th percentile
    and the median <!-- could be 25th -->
10. **Primarily onsite** - Teams that work remotely below the 5th
    percentile <!-- could be 75th -->
